Figures + Analysis

### 2019-04-24 r/Analysis.Rmd
4.23

@@

>>>>

Testing for variance in behavior variables among sites
```{r}

sum_id_stop <- sum_id %>%
  filter(species_code=="stop" & length_cm > 15 & length_cm < 30 & phase == "i") %>%
  mutate(site = as.factor(site))
sum_id_qup <- sum_id %>%
  filter(species_code=="qup" & length_cm > 15 & length_cm < 30 & phase == "i" ) %>%
  mutate(site = as.factor(site))

# feeding rates
leveneTest(fr ~ site, data = sum_id_stop) # variances are slightly heteroskedastic, p ~ 0.04, use KW instead of ANOVA
kruskal.test(fr ~ site, data = sum_id_stop) # significant variation across groups

leveneTest(fr ~ site, data = sum_id_qup) # variances are homogenous, p > 0.05, can use ANOVA
aov_fr_qup <- aov(fr ~ site, data = sum_id_qup) 
summary.aov(aov_fr_qup) # significant variation across sites

# bite rates
leveneTest(br ~ site, data = sum_id_stop) # variances are heteroskedastic, p < 0.05
kruskal.test(br ~ site, data = sum_id_stop) # no significant variation across groups

leveneTest(br ~ site, data = sum_id_qup) # variances are are heteroskedastic, p < 0.05
kruskal.test(br ~ site, data = sum_id_qup) # no significant variation

# time spent feeding
leveneTest(g_frac ~ site, data = sum_id_stop) # variances are homogenous, p > 0.05
aov_g_frac_qup <- aov(g_frac ~ site, data = sum_id_stop) 
summary.aov(aov_g_frac_qup) # significant variation across sites

leveneTest(g_frac ~ site, data = sum_id_qup) # variances are homogenous, p > 0.05
aov_g_frac_qup <- aov(g_frac ~ site, data = sum_id_qup) 
summary.aov(aov_g_frac_qup) # significant variation across sites

# foray length
leveneTest(for_bites ~ site, data = sum_id_stop) # variances are homogenous, p > 0.05
aov_for_bites_stop <- aov(for_bites ~ site, data = sum_id_stop) 
summary.aov(aov_for_bites_stop) # significant variation across sites

leveneTest(for_bites ~ site, data = sum_id_qup) # variances are homogenous, p > 0.05
aov_for_bites_qup <- aov(for_bites ~ site, data = sum_id_qup) 
summary.aov(aov_for_bites_qup) # significant variation across sites

```

@@

```{r}
# geom_point version
# keep this to get legend for panel
vg_facet <- ggplot(filter(sum_ssp_vg, species_code != "rbp" & phase == "i"), aes(x=factor(site, levels = sum_site$site), y=vg_mean)) +
    geom_point(stat = "identity", aes(color = fr_mean, size = ta_canopy), position = "dodge") +
    geom_errorbar(aes(ymin=vg_mean-vg_se, ymax=vg_mean+vg_se), width=.2,
                 position=position_dodge(.9)) +
    facet_grid(~species) +
    labs(title="Mean grazing impact by volume (initial phase)", 
         y="Grazing impact (cm3/hr)", 
         x="Site") +
    theme_bw() +
    theme(strip.text = element_text(face = "italic"), 
          axis.text.x = element_text(angle = 45, hjust = 1)
          )

vg_qup <- ggplot(filter(sum_ssp_vg, species_code == "qup" & phase == "i"), 
                 aes(x=factor(site, levels = sum_site$site), y=vg_mean)) +
    geom_point(stat = "identity", aes(color = fr_mean, size = ta_canopy), position = "dodge") +
    geom_errorbar(aes(ymin=vg_mean-vg_se, ymax=vg_mean+vg_se), width=.2,
                 position=position_dodge(.9)) +
  labs(y = expression('Grazing impact (cm'^3*'/hr)'), 
       x = "", 
       title = "S. vetula") +
  theme_bw() + 
  theme(plot.margin = margin(1, 0, 0, 5, unit = "pt"),
        axis.title.y = element_text(size=10),
        axis.text.x = element_text(angle = 45, hjust = 1, size=7),
        legend.position = "none",
        plot.title = element_text(hjust = 0.5, face = "italic")
        )

vg_stop <- ggplot(filter(sum_ssp_vg, species_code == "stop" & phase == "i"), 
                  aes(x=factor(site, levels = sum_site$site), y=vg_mean)) +
    geom_point(stat = "identity", aes(color = fr_mean, size = ta_canopy), position = "dodge") +    
    geom_errorbar(aes(ymin=vg_mean-vg_se, ymax=vg_mean+vg_se), width=.2,
                 position=position_dodge(.9)) +
  labs(y = "",
       x = "", 
       title = "S. viride") +
  theme_bw() + 
  theme(plot.margin = margin(1, 1, 0, 0, unit = "pt"),
        axis.text.x = element_text(angle = 45, hjust = 1, size=7),
        legend.position = "none",
        plot.title = element_text(hjust = 0.5, face = "italic")
        )

get_legend<-function(myggplot){
  tmp <- ggplot_gtable(ggplot_build(myggplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
  }
legend <- get_legend(vg_facet)

grid.arrange(
  arrangeGrob(vg_qup, vg_stop, ncol=2), 
              arrangeGrob(legend), 
              ncol=2, widths = c(5,1), heights = c(1))

g <- grid.arrange(
  arrangeGrob(vg_qup, vg_stop, ncol=2), 
              arrangeGrob(legend), 
              ncol=2, widths = c(5,1), heights = c(1))

ggsave(here("figs/bc_point_panel.png"),g)
```
